\textbf{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}\\Online Appendix (Not for publication)

### 2017-07-28 redaction/online_appendix_dhp2017.tex
addendum_modifsJH2707
modifsJH280717
Coquilles main text + redaction OA

\usepackage[flushleft]{threeparttable}
\makeatletter
\def\ps@pprintTitle{%
  \let\@oddhead\@empty
  \let\@evenhead\@empty
  \let\@oddfoot\@empty
  \let\@evenfoot\@oddfoot
}
\makeatother
\usepackage{adjustbox}
\usepackage{chngcntr}
\counterwithin{table}{section}
%\usepackage[round]{natbib}

@@

%Modèle additif seul
%+ableaux avec toutes les années en 3 digit et en 4 digit. Harmoniser la présentation des résultats (cf table 1 du papier)
%es résultats sur la version Hummels mais avec sa pondération: en annexe du papier? En online appendix?

@@

\newpage
%\section{\label{sec:addi}Additional Tables}

@@

\begin{table}[htbp]
  \centering
  \footnotesize{
  \caption{Transport costs estimates: Summary \label{sec_oa:add_only}}
  \begin{center}
    \begin{tabular}{l|cc|cc}
      \hline \hline
    \multicolumn{5}{c}{Mean value over 1974-2013}   \\
    \# digit & \multicolumn{2}{c}{3 digits} & \multicolumn{2}{c}{4 digits ($^\ast$)} \\ \hline
    Mode  & Vessel & Air ($^{\ast \ast}$) & Vessel & Air \\ \hline
    \multicolumn{5}{l}{\textbf{With only Additive Transport Costs} ($\widehat{t}^{add}$, in \%)}  \\ \hline
    Mean  & 9.2 & 5.1 & 8.0 & 5.8 \\
    Median & 5.7 & 2.4 & 5.5 & 2.5 \\ \hline

       \multicolumn{5}{l}{\textbf{Data} ($p/\widetilde{p}$, in \%) } \\ \hline
        Mean & 5.3 & 5.0& 5.6&3.9 \\
        Median & 4.3 & 2.0 & 4.4& 1.9 \\ \hline
        \# obs. & 29279 & 28207 & 29317 & 27680 \\
    \# origin country & 188 & 191 & 188 & 189 \\
    \# products & 230 & 211 & 666 & 567 \\  \hline \hline
  \end{tabular}
    \end{center}}
\parbox[l]{10cm}{\tiny{Notes: Statistics are obtained weighting each observation by its value relative to total trade flows. The additive term is expressed in fraction of fas price. ($^\ast$): Four 4-digit estimation: 0n selected years. ($^{\ast \ast}$): 1989 omitted in 3-digit estimation for air.}}
\end{table}%

%
%XXXXXX
%
%
%			SECTION 2 / ALTERNATIVE MEASURES OF FIRM PERFORMANCE
%			
%			
%					
%XXXXXX
%
%
%
%\subsection{At a more disaggregated level}

\textbf{A mon avis, a mettre en online appendix. Expliquer comment se fait la decomposition en secteurs primaire/manuf.}

@@

\textbf{A commenter. A mettre en Online Appendix?}

\subsection{Detailed Results \label{secoa:detailed}}
\setcounter{table}{0}
\renewcommand{\thetable}{B.\arabic{table}}

\subsubsection{3-Digits Level}

\subsubsection{4-Digits Level}

@@

>>>>

\usepackage[flushleft]{threeparttable}

%\usepackage{titling}

%\setlength{\droptitle}{-10em}   % This is your set screw

\makeatletter
\def\ps@pprintTitle{%
  \let\@oddhead\@empty
  \let\@evenhead\@empty
  \let\@oddfoot\@empty
  \let\@evenfoot\@oddfoot
}
\makeatother
\usepackage{adjustbox}
\usepackage{chngcntr}
\counterwithin{table}{section}
%\usepackage[round]{natbib}

@@

%Modèle additif seul DONE
%+Tableaux avec toutes les années en 3 digit DONE
% Tableaux avec toutes les années en 4 digit ???
%Harmoniser la présentation des résultats (cf table 1 du papier) DONE
%Les résultats sur la version Hummels mais avec sa pondération: en annexe du papier? En online appendix? DONE, mais à compléter

@@

\newpage

%
%
%
%
%			SECTION A / ADDITIVE ONLY
%			
%			
%				
%
%

@@

\begin{table}[htbp]
  \centering
  \footnotesize{
  \caption{Transport costs estimates : Summary\label{sec_oa:add_only}}
  \begin{center}
    \begin{tabular}{l|cc|cc}
      \hline \hline
    \multicolumn{5}{c}{Mean value over 1974-2013}   \\
    \# digit & \multicolumn{2}{c}{3 digits} & \multicolumn{2}{c}{4 digits ($^\ast$)} \\ \hline
    Mode  & Vessel & Air ($^{\ast \ast}$) & Vessel & Air \\ \hline
    \multicolumn{5}{l}{\textbf{With only Additive Transport Costs} ($\widehat{t}^{add}$, in \%)}  \\ \hline
    Mean  & 9.2 & 5.1 & 8.0 & 5.8 \\
    Median & 5.7 & 2.4 & 5.5 & 2.5 \\ \hline

       \multicolumn{5}{l}{\textbf{Data} ($p/\widetilde{p}$, in \%) } \\ \hline
        Mean & 5.3 & 5.0& 5.6&3.9 \\
        Median & 4.3 & 2.0 & 4.4& 1.9 \\ \hline
        \# obs. & 29279 & 28207 & 29317 & 27680 \\
    \# origin country & 188 & 191 & 188 & 189 \\
    \# products & 230 & 211 & 666 & 567 \\  \hline \hline
  \end{tabular}
    \end{center}}
\parbox[l]{10cm}{\tiny{Notes: Statistics are obtained weighting each observation by its value relative to total trade flows. The additive term is expressed in fraction of fas price. ($^\ast$): Four 4-digit estimation: on selected years. ($^{\ast \ast}$): 1989 omitted in 3-digit estimation for air.}}
\end{table}%

%
%
%
%
%			SECTION B / DETAILED RESULTS
%			
%			
%				
%
%

\newpage
%\subsection{Detailed Results \label{secoa:detailed}}
\setcounter{table}{0}
\renewcommand{\thetable}{B.\arabic{table}}

\subsection{Transport Cost Estimates: Yearly Detailed Results}

\subsubsection{3-Digits Level Product Classification}
\begin{landscape}
\begin{table}[htbp]
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
  %\centering
\caption{Air: Transport costs estimates, all years, 3-digit}
\begin{center}
\scalebox{0.85}{\begin{tabular}{lcccccccccccccccccccc}
\hline
\hline
Year  & 1974  & 1975  & 1976  & 1977  & 1978  & 1979  & 1980  & 1981  & 1982  & 1983  & 1984  & 1985  & 1986  & 1987  & 1988  & 1989  & 1990  & 1991  & 1992  & 1993 \\
\hline
\multicolumn{20}{l}{\textbf{Model (A) - With only Ad-Valorem Trade Costs} ($\widehat{\tau}^{ice}$, in \%)} \\
\hline
Mean  & 6.9   & 7.5   & 7.2   & 7.7   & 6.9   & 6.1   & 5.4   & 6.0   & 6.4   & 6.9   & 7.2   & 6.1   & 6.4   & 6.6   & 5.7   & 5.3   & 5.0   & 5.1   & 4.9   & 5.1 \\
Median & 5.4   & 6.4   & 6.9   & 7.1   & 6.3   & 5.3   & 3.8   & 4.9   & 5.3   & 6.1   & 6.7   & 5.5   & 5.9   & 6.3   & 5.3   & 4.6   & 4.4   & 4.5   & 4.5   & 4.4 \\
\hline
\multicolumn{20}{l}{\textbf{Model (B) - With Additive \& Ad-Valorem Trade Costs} }\\ \hline
\multicolumn{20}{l}{\textit{Ad-valorem term ($\widehat{\tau}^{adv}$, in \%)} }   \\ 
\hline
Mean  & 3.6   & 3.7   & 3.9   & 3.8   & 3.2   & 3.0   & 2.3   & 2.8   & 2.8   & 2.6   & 3.3   & 2.5   & 3.2   & 2.6   & 3.1   & 3.1   & 2.4   & 2.7   & 2.2   & 2.4 \\
Median & 2.7   & 2.7   & 2.9   & 2.7   & 2.1   & 2.4   & 1.6   & 1.8   & 1.9   & 1.9   & 2.7   & 1.8   & 2.1   & 2.0   & 2.0   & 1.9   & 1.6   & 1.5   & 1.5   & 1.6 \\

\hline
\multicolumn{20}{l}{\textit{Additive term ($\widehat{t}^{add}/\widetilde{p}$, in \%)} }   \\ 
\hline
Mean  & 2.6   & 3.0   & 2.3   & 3.1   & 2.6   & 2.1   & 2.0   & 2.0   & 2.3   & 2.8   & 2.5   & 2.8   & 2.6   & 2.9   & 1.7   & 4.6   & 1.8   & 1.8   & 1.9   & 1.9 \\
Median & 1.1   & 1.2   & 0.9   & 1.3   & 1.1   & 0.7   & 0.5   & 0.6   & 0.8   & 1.0   & 1.0   & 1.3   & 1.3   & 1.5   & 1.0   & 0.7   & 0.8   & 0.6   & 0.9   & 0.8 \\
\hline
\# observations & 14955 & 15299 & 11397 & 10707 & 15222 & 15684 & 16118 & 16864 & 17322 & 18180 & 20644 & 19908 & 20695 & 20793 & 24663 & 25197 & 24958 & 25156 & 26191 & 28296 \\

%%%%%%%%%%%%%%%%2nd part of the table

\hline\hline
\multicolumn{20}{c}{ }  \\
\multicolumn{20}{c}{Continued}  \\
\hline\hline

Year  & 1994  & 1995  & 1996  & 1997  & 1998  & 1999  & 2000  & 2001  & 2002  & 2003  & 2004  & 2005  & 2006  & 2007  & 2008  & 2009  & 2010  & 2011  & 2012  & 2013 \\
\hline
\multicolumn{20}{l}{\textbf{Model (A) - With only Ad-Valorem Trade Costs} ($\widehat{\tau}^{ice}$, in \%)} \\
\hline
Mean  & 4.6   & 4.6   & 4.2   & 4.1   & 3.8   & 3.8   & 3.6   & 3.5   & 3.8   & 3.9   & 4.0   & 4.1   & 3.9   & 4.1   & 4.1   & 4.0   & 4.2   & 3.9   & 3.7   & 3.4 \\
Median & 3.7   & 3.8   & 3.1   & 3.0   & 2.7   & 2.8   & 2.5   & 2.4   & 2.7   & 2.6   & 2.9   & 3.1   & 2.7   & 3.0   & 3.2   & 3.0   & 3.4   & 3.1   & 3.0   & 2.9 \\
\hline
\multicolumn{20}{l}{\textbf{Model (B) - With Additive \& Ad-Valorem Trade Costs} }\\ \hline
\multicolumn{20}{l}{\textit{Ad-valorem term ($\widehat{\tau}^{adv}$, in \%)} }   \\ 
\hline
Mean  & 2.3   & 2.1   & 1.9   & 1.8   & 1.8   & 1.8   & 1.7   & 1.6   & 1.6   & 1.9   & 1.9   & 2.0   & 1.8   & 2.3   & 2.3   & 2.3   & 2.6   & 2.2   & 2.2   & 1.7 \\
Median & 1.3   & 1.4   & 1.4   & 1.3   & 1.3   & 1.5   & 1.2   & 1.1   & 1.2   & 1.4   & 1.4   & 1.6   & 1.4   & 1.9   & 1.9   & 1.8   & 2.2   & 1.7   & 1.9   & 1.7 \\
\hline
\multicolumn{20}{l}{\textit{Additive term ($\widehat{t}^{add}/\widetilde{p}$, in \%)} }   \\
\hline
Mean  & 1.7   & 1.6   & 1.5   & 1.5   & 1.4   & 1.4   & 1.3   & 1.3   & 1.6   & 1.4   & 1.5   & 1.4   & 1.3   & 1.2   & 1.2   & 1.2   & 1.1   & 1.1   & 0.9   & 1.0 \\
Median & 0.8   & 0.7   & 0.6   & 0.6   & 0.5   & 0.5   & 0.5   & 0.5   & 0.5   & 0.5   & 0.6   & 0.5   & 0.5   & 0.5   & 0.5   & 0.5   & 0.4   & 0.4   & 0.4   & 0.5 \\
\hline
\# observations & 29948 & 31037 & 32187 & 33502 & 33492 & 33523 & 35027 & 34885 & 35159 & 35891 & 36990 & 41806 & 42554 & 40858 & 40159 & 38275 & 40279 & 41190 & 40909 & 39351 \\

\hline
\hline
\end{tabular}}%

\end{center}
\label{tab_oa:result_air_ally3}%
\end{table}%
\end{landscape}

\begin{landscape}
\begin{table}[htbp]
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
\caption{Vessel: Transport costs estimates, all years, 3-digit}
\begin{center}
\scalebox{0.85}{\begin{tabular}{lcccccccccccccccccccc}
\hline
\hline
Year  & 1974  & 1975  & 1976  & 1977  & 1978  & 1979  & 1980  & 1981  & 1982  & 1983  & 1984  & 1985  & 1986  & 1987  & 1988  & 1989  & 1990  & 1991  & 1992  & 1993 \\
\hline
\multicolumn{20}{l}{\textbf{Model (A) - With only Ad-Valorem Trade Costs} ($\widehat{\tau}^{ice}$, in \%)} \\
\hline
Mean  & 9.8   & 9.9   & 8.9   & 8.3   & 8.1   & 7.5   & 6.5   & 6.0   & 6.3   & 7.0   & 7.0   & 6.9   & 6.7   & 6.2   & 6.1   & 5.7   & 5.7   & 5.5   & 5.0   & 5.2 \\
Median & 9.6   & 8.5   & 8.0   & 7.3   & 7.1   & 6.5   & 5.5   & 5.0   & 5.9   & 5.7   & 6.1   & 6.3   & 7.0   & 6.3   & 5.7   & 4.8   & 4.6   & 4.4   & 4.2   & 4.7 \\
\hline
\multicolumn{20}{l}{\textbf{Model (B) - With Additive \& Ad-Valorem Trade Costs} }\\ \hline
\multicolumn{20}{l}{\textit{Ad-valorem term ($\widehat{\tau}^{adv}$, in \%)} }   \\  
\hline
Mean  & 5.4   & 4.8   & 5.4   & 5.2   & 5.9   & 4.6   & 3.1   & 3.3   & 3.4   & 4.2   & 4.1   & 4.0   & 3.9   & 3.6   & 4.0   & 3.0   & 3.3   & 3.0   & 2.6   & 2.9 \\
Median & 4.9   & 4.1   & 4.8   & 4.4   & 5.4   & 4.0   & 2.4   & 2.9   & 2.9   & 3.9   & 3.5   & 3.6   & 3.6   & 3.0   & 3.5   & 2.6   & 2.8   & 2.7   & 2.3   & 2.6 \\
\multicolumn{20}{l}{\textit{Additive term ($\widehat{t}^{add}/\widetilde{p}$, in \%)} }   \\         
\hline
Mean  & 5.1   & 5.5   & 3.5   & 3.5   & 2.5   & 3.1   & 3.4   & 2.9   & 3.5   & 2.9   & 3.2   & 3.2   & 2.9   & 2.8   & 2.4   & 2.9   & 2.7   & 2.8   & 2.7   & 2.7 \\
Median & 2.9   & 3.6   & 1.9   & 1.7   & 1.2   & 1.7   & 2.3   & 1.5   & 2.3   & 2.0   & 2.3   & 2.1   & 1.8   & 1.8   & 1.3   & 2.0   & 1.7   & 1.7   & 1.8   & 1.6 \\
\hline
\# observations & 19007 & 18710 & 13615 & 12826 & 16601 & 17274 & 17356 & 17788 & 18075 & 18883 & 21650 & 23348 & 23729 & 23626 & 27661 & 29106 & 28383 & 28095 & 29050 & 30839 \\ %%%%%%%%%%%%%%%%2nd part of the table

\hline\hline
\multicolumn{20}{c}{ }  \\
\multicolumn{20}{c}{Continued}  \\
\hline\hline

Year  & 1994  & 1995  & 1996  & 1997  & 1998  & 1999  & 2000  & 2001  & 2002  & 2003  & 2004  & 2005  & 2006  & 2007  & 2008  & 2009  & 2010  & 2011  & 2012  & 2013 \\
\hline
\multicolumn{20}{l}{\textbf{Model (A) - With only Ad-Valorem Trade Costs} ($\widehat{\tau}^{ice}$, in \%)} \\
\hline
Mean  & 5.2   & 5.1   & 4.8   & 4.7   & 4.8   & 5.0   & 5.1   & 5.0   & 4.8   & 5.2   & 5.4   & 5.5   & 4.8   & 4.7   & 4.4   & 4.3   & 4.0   & 3.5   & 3.6   & 3.6 \\
Median & 4.1   & 4.3   & 3.9   & 3.9   & 3.9   & 4.5   & 4.9   & 4.6   & 4.1   & 4.8   & 5.1   & 4.9   & 4.2   & 4.2   & 3.8   & 4.1   & 3.6   & 3.0   & 3.1   & 3.3 \\
\hline
\multicolumn{20}{l}{\textbf{Model (B) - With Additive \& Ad-Valorem Trade Costs} }\\ \hline
\multicolumn{20}{l}{\textit{Ad-valorem term ($\widehat{\tau}^{adv}$, in \%)} }   \\        
\hline
Mean  & 2.6   & 2.8   & 2.6   & 2.5   & 2.2   & 2.5   & 2.5   & 2.7   & 2.4   & 2.4   & 2.7   & 2.6   & 2.3   & 2.5   & 2.1   & 2.2   & 1.9   & 1.8   & 1.8   & 2.2 \\
Median & 2.2   & 2.5   & 2.2   & 2.2   & 1.9   & 2.1   & 2.1   & 2.6   & 2.3   & 1.9   & 2.8   & 2.2   & 1.9   & 2.3   & 1.8   & 2.0   & 1.8   & 1.6   & 1.4   & 1.8 \\
\hline
\multicolumn{20}{l}{\textit{Additive term ($\widehat{t}^{add}/\widetilde{p}$, in \%)} }   \\
\hline
Mean  & 2.9   & 2.7   & 2.5   & 2.5   & 3.2   & 2.8   & 2.8   & 2.4   & 2.6   & 3.2   & 2.9   & 3.0   & 2.8   & 2.4   & 2.4   & 2.1   & 2.5   & 1.9   & 1.9   & 1.5 \\
Median & 2.0   & 1.8   & 1.6   & 1.3   & 2.0   & 2.0   & 2.2   & 1.6   & 2.0   & 2.5   & 1.9   & 2.2   & 1.9   & 1.8   & 2.1   & 1.7   & 1.9   & 1.6   & 1.6   & 0.8 \\
\hline
\# observations & 31865 & 32146 & 32344 & 33181 & 33986 & 34585 & 36090 & 36407 & 37255 & 37672 & 37757 & 41431 & 41763 & 39604 & 38950 & 37332 & 37748 & 38562 & 38387 & 38473 \\
\hline
\hline
\end{tabular}}

\end{center}
\label{tab_oa:result_vessel_ally3}%
\end{table}
\end{landscape}

\setcounter{table}{0}
\renewcommand{\thetable}{C.\arabic{table}}

\subsection{Eliminating the composition effects: Primary vs. Maufacturing sector} \label{sec_oa:comp-effects}

%\todo{A mon avis, a mettre en online appendix. Expliquer comment se fait la decomposition en secteurs primaire/manuf.}

@@

%\textbf{A commenter. A mettre en Online Appendix?}

[TO BE COMPLETED]

@@

\subsubsection{4-Digits Level Product Classification}

\begin{landscape}
\begin{table}[htbp]
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
\caption{Air: Transport costs estimates, all years, 4-digit}
\begin{center}
\scalebox{0.85}{\begin{tabular}{lcccccccccccccccccccc}
\hline
\hline

%%%%%%%%%%%%%%%%2nd part of the table

\hline\hline
\multicolumn{20}{c}{ }  \\
\multicolumn{20}{c}{Continued}  \\
\hline\hline

\hline
\hline
\end{tabular}}

\end{center}
\label{tab_oa:result_vessel_ally3}%
\end{table}
\end{landscape}
